### 2014-04-11 ApTranscriptome_TR.Rmd
Version 0.2 of manuscript finished and sent to group

```{r A22_high_wilcoxon}
wilcox.test(A22.high.transcripts$A22.opt, A22.high.transcripts$Ar.opt, alternative = "two.sided", paired = TRUE, conf.int = TRUE)
```

@@

# Wilcoxon signed rank-test
wilcox.test(Ar.low.transcripts$A22.opt, Ar.low.transcripts$Ar.opt, alternative = "two.sided", paired = TRUE, conf.int = TRUE)
```

@@

# T-test comparing standard deviation of expression between colonies
t1 <- t.test(Ar.int.sd$exp_sd, A22.int.sd$exp_sd)
```

@@

```{r annotation}
# add annotation information
setkey(annotationtable, Sequence.Name)
signif.transcripts <- data.table(signif.transcripts)
setkey(signif.transcripts, Transcript)
signif.transcripts <- annotationtable[signif.transcripts]
setnames(signif.transcripts, "Sequence.Name", "Transcript")
```

@@

# perform enrichment analysis using parentchild method
Ap.BP.resultParentChild <- runTest(Ap.BP.GOdata, statistic = 'fisher', algorithm = 'parentchild')
# Ap.BP.resultParentChild

# table results
Ap.BP.ResTable <- GenTable(Ap.BP.GOdata, parentchild = Ap.BP.resultParentChild, topNodes = 82)
dim(Ap.BP.ResTable)
#pandoc.table(Ap.BP.ResTable)

@@

# Run GSEA
Ap.high.gsea <- gsea(genelist = Ap.geneList.high, geneID2GO = geneID2GO, plotpath = "results/Ar_int_BP_topGO_sig_nodes.pdf")
#pandoc.table(Ap.high.gsea)
```

@@

# Run GSEA
Ap.low.gsea <- gsea(genelist = Ap.geneList.low, geneID2GO = geneID2GO)
#pandoc.table(Ap.low.BP.ResTable)
```

@@

# Run GSEA
Ap.bim.gsea <- gsea(genelist = Ap.geneList.bim, geneID2GO = geneID2GO)
#pandoc.table(Ap.bim.gsea)
```

@@

# Run GSEA
Ap.int.gsea <- gsea(genelist = Ap.geneList.int, geneID2GO = geneID2GO)
#pandoc.table(Ap.int.gsea)
```

@@

# Smooth plot, expression against temp, faceted by colony
trp2 <- ggplot(resp.TPM.dt.sub[high.stress.terms$Transcript], aes(x=val, y=TPM.scaled, group=Transcript)) + 
  geom_smooth(method = "lm", formula = y ~ poly(x, 2)) + 
  facet_grid(. ~ colony) + 
  scale_y_continuous(name="Expression (scaled)") +
  scale_x_continuous(name=expression(paste("Temperature ", degree, "C")))
print(trp2)
```

@@

```{r rData, echo=FALSE}
# save RData for manuscript file
save(Ap.type.table, Ap.df, file = "ms.RData")
```

>>>>

```{r A22_high_wilcoxon}
(w1 <- wilcox.test(A22.high.transcripts$A22.opt, A22.high.transcripts$Ar.opt, alternative = "two.sided", paired = TRUE, conf.int = TRUE))
```

@@

# Wilcoxon signed rank-test
(w2 <- wilcox.test(Ar.low.transcripts$A22.opt, Ar.low.transcripts$Ar.opt, alternative = "two.sided", paired = TRUE, conf.int = TRUE))
```

@@

# T-test comparing standard deviation of expression between colonies
(t1 <- t.test(Ar.int.sd$exp_sd, A22.int.sd$exp_sd, alternative = "two.sided"))
```

@@

```{r annotation}
setkey(annotationtable, Sequence.Name)
signif.transcripts <- data.table(signif.transcripts)
setkey(signif.transcripts, Transcript)
signif.transcripts <- annotationtable[signif.transcripts]
setnames(signif.transcripts, "Sequence.Name", "Transcript")
```

@@

# perform enrichment analysis using parentchild method
Ap.BP.resultParentChild <- runTest(Ap.BP.GOdata, statistic = 'fisher', algorithm = 'parentchild')
Ap.BP.resultParentChild

# table results
Ap.BP.ResTable <- GenTable(Ap.BP.GOdata, parentchild = Ap.BP.resultParentChild, topNodes = 113)
dim(Ap.BP.ResTable)
#pandoc.table(Ap.BP.ResTable)

@@

# Run GSEA
Ap.high.gsea <- gsea(genelist = Ap.geneList.high, geneID2GO = geneID2GO, plotpath = "results/Ar_int_BP_topGO_sig_nodes.pdf")
#pandoc.table(Ap.high.gsea)
# output for Revigo
write.table(Ap.high.gsea[,"GO.ID"], file = "results/Ap_high_gsea.txt", row.names = FALSE, sep = "\t", quote = FALSE)
```

@@

# Run GSEA
Ap.low.gsea <- gsea(genelist = Ap.geneList.low, geneID2GO = geneID2GO)
#pandoc.table(Ap.low.BP.ResTable)
write.table(Ap.low.gsea[,"GO.ID"], file = "results/Ap_low_gsea.txt", row.names = FALSE, sep = "\t", quote = FALSE)
```

@@

# Run GSEA
Ap.bim.gsea <- gsea(genelist = Ap.geneList.bim, geneID2GO = geneID2GO)
#pandoc.table(Ap.bim.gsea)
write.table(Ap.bim.gsea[,"GO.ID"], file = "results/Ap_bim_gsea.txt", row.names = FALSE, sep = "\t", quote = FALSE)
```

@@

# Run GSEA
Ap.int.gsea <- gsea(genelist = Ap.geneList.int, geneID2GO = geneID2GO)
#pandoc.table(Ap.int.gsea)
write.table(Ap.int.gsea[,"GO.ID"], file = "results/Ap_int_gsea.txt", row.names = FALSE, sep = "\t", quote = FALSE)
```

@@

# Smooth plot, expression against temp, faceted by colony
png("results/GO_stress_High.png")
trp2 <- ggplot(resp.TPM.dt.sub[high.stress.terms$Transcript], aes(x=val, y=TPM.scaled, group=Transcript)) + 
  geom_smooth(method = "lm", formula = y ~ poly(x, 2)) + 
  facet_grid(. ~ colony) + 
  scale_y_continuous(name="Expression (scaled)") +
  scale_x_continuous(name=expression(paste("Temperature ", degree, "C")))
print(trp2)
dev.off()
```

@@

```{r rData, echo=FALSE}
# save RData for manuscript file
save(Ap.type.table, Ap.df, w1, w2, file = "ms.RData")
```
